Improving the Efficiency of Dislocality Constraints for an Automated Software Mapping in Safety-Critical Systems

### 2017-12-18 paper.tex
Added some stuff

\begin{itemize}
\item In order to ensure a reliability / redundancy work properly - it is essential to ensure is differences
\item Differences in the deployment of redundant software components to make sure that the errors do not appear in the same manner at the same location (zonal effects)
\item Dislocality is a typical constraint in ASSIST to express these differences
\item Simple Modeling approach for a CSP (location variables)
\item Use allDiffererent constraint - straight forward
\end{itemize}

>>>>

\begin{itemize}
\item In order to ensure a reliability / redundancy work properly - it is essential to ensure is differences
\item Differences in the deployment of redundant software components to make sure that the errors do not appear in the same manner at the same location (zonal effects)
\item Dislocality is a typical constraint in ASSIST to express these differences
\item Simple Modeling approach for a CSP (location variables)
\item Use allDiffererent constraint - straight forward
\item Reality: AllDifferent for List of Lists
\item Example to describe the differences
\end{itemize}

\section{Modeling Advanced Dislocality Constraints}

\begin{itemize}
\item Based on available tools - one option is the recursive approach
\item Implementation is straight forward, but it requires a lot of constraints - slow in practice
\item Another option is to react on instantiation only and remove unwanted solutions - weak in propagation
\item Last Option is to combine inst-only approach with int-values union and alldifferent
\end{itemize}

\section{Experiments}

\begin{itemize}
\item Synthetic example generator 
\item 10/20 Examples were generated with a parameter domain ...
\item Search with the same strategies DomWD, minValueFirst
\item iMac 5k, 64 GB RAM, Choco 4.0.6
\end{itemize}

\section{Results}

\begin{itemize}
\item Show results for var count, constraint count
\item Show results for resolution time
\item Show results for backtracks and fails
\end{itemize}

\section{Conclusions}

I am a summary
